Mbh-n paper

### 2015-10-20 papers/ellicular/ellicular.tex
tue

\begin{abstract}
{\bf The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies. 
%with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio of an early-type galaxy can assume any positive value,  
but in practice studies often consider only spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii, 
creating an inner ``bulge'' as observed in most spiral galaxies. 
Here we show that decompositions in which the disc remains embedded within the spheroid, 
labelled by some as ``unphysical'',  
correctly reproduce both the photometric and kinematic properties of early-type galaxies 
%intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
with intermediate-scale discs. 
Intermediate-scale discs have often been confused with large-scale discs, and modelled accordingly; 
when this happens, the spheroid luminosity is considerably underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of galaxies with intermediate-scale discs (e.g.~Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
We show that when galaxies with intermediate-scale discs are correctly modelled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes. }

@@

Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of stellar discs in early-type galaxies. \\

@@

i.e.~a spheroid-dominated central fast rotator that becomes slow rotating beyond one half-light radius, and  

@@

% \subsection{Ellicular galaxies in the Hubble grid}
% The existence of the oft-overlooked, intermediate-scale discs
% exposes a likely continuum of disc sizes in early-type
% galaxies, as opposed to a dichotomy of nuclear discs versus large-scale
% discs. The presence of these intermediate-scale discs also blurs the
% distinction between elliptical (E) and lenticular (S0: $\epsilon = 1-b/a > 0.7$, \citealt{hubble1936,sandage1961}) galaxies and
% arguably creates the need for a new subclass which bridges this
% divide.  While expanding the galaxy nomenclature beyond ellipticals
% with possible nuclear discs, and lenticulars with large-scale discs,
% to include something like \emph{elliculars} with intermediate-scale
% discs will be helpful for distinguishing among 
% early-type galaxies with different disc scale-lengths, it should be
% remembered that just as portions of the electromagnetic spectrum are
% labelled according to their different wavelengths, there is still an
% underlying continuum.  Similarly, binning early-type galaxies as
% either a fast-rotator (FR) or a slow-rotator (SR) can hide the fact
% that a continuum exists.  Importantly, in the case of early-type
% galaxies with intermediate-scale discs, this particular
% rotation-based classification depends on the galaxy's radial range probed, 
% changing from FR to SR as the radial extent is sufficiently increased. 
% There is thus a need for more than two bins (E vs. S0, or FR vs. SR) 
% and a continuum in the (Hubble-Jeans)-like classification schemes \citep{vandenbergh1997,sandage2005}. \\
% It has been argued that the classification
% scheme for ``elliptical'' galaxies should not be their apparent axis ratio
% as seen on the plane of the sky (E0--E7), 
% because this depends on the viewing angle rather than being intrinsic to the galaxy. 
% Obviously when dealing with intermediate-scale discs, the boxy/discy shape of the isophotes is a function of both radius and disc inclination, 
% making a single isophote shape parameter problematic and particularly inappropriate for the classification task at hand.
% Section 4 of \cite{kormendybender1996} points out additional complications. 
% Instead, early-type galaxies would be better quantified by their spheroid-to-total flux ratio, with a
% continuum from pure elliptical galaxies to disc-dominated lenticular
% galaxies (Figure \ref{fig:grid}).  \\
% While spiral galaxies display a range of spheroid-to-total flux ratios
% from 0 to $\sim$3/4 (e.g.~\citealt{grahamworley2008}, and references
% therein), lenticular galaxies typically display a range from
% $\sim$3/4 to $\sim$0.1 \citep{laurikainen2010}.  This spheroid-to-total flux
% ratio is widely recognised as an important quantity, and its broad range observed in
% lenticular galaxies recently led to a re-introduction of 
% \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976})
% Hubble comb, in which both late-type galaxies (i.e.~spiral galaxies)
% and lenticular galaxies form separate arms of an expanded Hubble-Jeans tuning
% fork, with an additional arm for disc galaxies hosting anaemic spiral
% patterns \citep{cappellari2011kmdr,kormendybender2012}.  
% However because every spiral Hubble type (e.g.~Sa, Sb, Sc), not just the S0 galaxies, 
% has a broad range of spheroid-to-total ratio, and because this information is not captured by the Hubble comb, 
% a grid of spiral morphological type (predominantly determined by the spiral
% arms) versus spheroid-to-total ratio can also be useful for classifying galaxies.  \\
% In Figure \ref{fig:grid} we show the location of galaxies with intermediate-scale
% discs in such a ``Hubble grid'', which is effectively the quantitative scheme used by  
% \cite{boroson1981}, \cite{kent1985}, \cite{kodaira1986}, \cite{simiendevaucouleurs1986} 
% in which each galaxy type displays a range of spheroid-to-total flux ratio.
% Rather than a scheme in which the morphological type (a, b, c,
% etc.) changes if the spheroid-to-total ratio changes -- as in the Hubble comb -- here
% the galaxy type is linked to the nature and winding of the spiral arms
% which has been the primary criteria used to classify spiral galaxies
% over the last half century \citep{sandage1961}.  
% Allowing for the varying spheroid-to-total ratio among each galaxy type, 
% the Hubble grid helps to reveal how ellicular galaxies unify the early-type sequence and compare with late-type galaxies.

% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\columnwidth]{Hubblegrid.pdf}
% \caption{The Hubble grid \citep{graham2014review},
% which uses the mean pitch angle of the arms in spiral galaxies to define their morphological type.
% Ellicular (ES) galaxies are intermediate between elliptical (E) and lenticular (S0) galaxies. }
% \label{fig:grid}
% \end{center}
% \end{figure}

\section{Summary and conclusions}
{\bf Early-type galaxies display a continuous distribution of spheroid-to-total flux ratios, 
going from disc-less, ``pure'' elliptical galaxies (slow rotators) 
to disc-dominated lenticular galaxies (central fast rotators that continue to be fast rotating also beyond one half-light radius) 
(e.g.~\citealt{cappellari2011}). 
%\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
%vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
%simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,
%bendersaglia1999}\footnote{Many past studies were hampered by bulge/disc decompositions which forced an $R^{1/4}$ model for the bulge component 
%and thus obtained spurious bulge-to-disc ratios, and from the \emph{IRAF} task {\tt ellipse} which does not report the correct deviations of isophotes 
%from ellipses \citep{ciambur2015}.}. 
In between these two extremes lie galaxies with intermediate-scale discs 
(spheroid dominated central fast rotators that become slow rotating in their outer regions), 
i.e.~discs of kiloparsec-size that remain ``embedded'' within the spheroidal component of the galaxy 
and do not dominate the galaxy light at large radii as large-scale discs do. }
While this is likely known to some readers, 
the surge of papers presenting galaxy decompositions which are not aware of this reality 
has created a pressing need for this reminder. 
We have shown that the light distribution of galaxies with intermediate-scale discs can be accurately described 
with a simple spheroid + disc (+ optional nuclear component) model, 
without the need for the addition of a bright envelope-component. \\
Our decompositions correctly reproduce both the photometric (surface brightness and ellipticity profiles) 
and kinematic (specific angular momentum profile) properties of nine intermediate-scale disc galaxies. 
Four of these nine galaxies (Mrk 1216, NGC 1271, NGC 1277, NGC 1332) and one additional elliptical galaxy (NGC 4291) 
had previously been claimed to be extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
However, here we have demonstrated that, when correctly modelled, 
these five galaxies all reside well within the scatter of the correlation, 
i.e. they do not host over-massive black holes. 
This serves to strengthen the (black hole mass)-(spheroid mass) relation, 
and rules out the need for exotic formation scenarios.

>>>>

\begin{abstract}
{\bf The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies. 
%with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio of an early-type galaxy can assume any positive value,  
but in practice studies often consider only spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii, 
creating an inner ``bulge'' as observed in most spiral galaxies. 
Here we show that decompositions in which the disc remains embedded within the spheroid, 
labelled by some as ``unphysical'',  
correctly reproduce both the photometric and kinematic properties of early-type galaxies 
%intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
with intermediate-scale discs. 
Intermediate-scale discs have often been confused with large-scale discs, and modelled accordingly; 
when this happens, the spheroid luminosity is considerably underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of galaxies with intermediate-scale discs (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
We show that when these galaxies are correctly modelled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes. }

@@

Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of a stellar disc in an early-type galaxy. \\

@@

i.e.~a spheroid-dominated central fast rotator that becomes slow rotating beyond $1-2$ half-light radii, and  

@@

  \subsection{Ellicular galaxies in the Hubble grid}
  The existence of the oft-overlooked, intermediate-scale discs
  exposes a likely continuum of disc sizes in early-type
  galaxies, as opposed to a dichotomy of nuclear discs versus large-scale
  discs. The presence of these intermediate-scale discs also blurs the
  distinction between elliptical (E) and lenticular (S0: $\epsilon = 1-b/a > 0.7$, \citealt{hubble1936,sandage1961}) galaxies and
  arguably creates the need for a new subclass which bridges this
  divide.  While expanding the galaxy nomenclature beyond ellipticals
  with possible nuclear discs, and lenticulars with large-scale discs,
  to include something like \emph{elliculars} with intermediate-scale
  discs will be helpful for distinguishing among 
  early-type galaxies with different disc scale-lengths, it should be
  remembered that just as portions of the electromagnetic spectrum are
  labelled according to their different wavelengths, there is still an
  underlying continuum.  Similarly, binning early-type galaxies as
  either a fast-rotator (FR) or a slow-rotator (SR) can hide the fact
  that a continuum exists.  Importantly, in the case of early-type
  galaxies with intermediate-scale discs, this particular
  rotation-based classification depends on the galaxy's radial range probed, 
  changing from FR to SR as the radial extent is sufficiently increased. 
  There is thus a need for more than two bins (E vs. S0, or FR vs. SR) 
  and a continuum in the (Hubble-Jeans)-like classification schemes \citep{vandenbergh1997,sandage2005}. \\
  It has been argued that the classification
  scheme for ``elliptical'' galaxies should not be their apparent axis ratio
  as seen on the plane of the sky (E0--E7), 
  because this depends on the viewing angle rather than being intrinsic to the galaxy. 
  Obviously when dealing with intermediate-scale discs, the boxy/discy shape of the isophotes is a function of both radius and disc inclination, 
  making a single isophote shape parameter problematic and particularly inappropriate for the classification task at hand.
  Section 4 of \cite{kormendybender1996} points out additional complications. 
  Instead, early-type galaxies would be better quantified by their spheroid-to-total flux ratio, with a
  continuum from pure elliptical galaxies to disc-dominated lenticular
  galaxies (Figure \ref{fig:grid}).  \\
  While spiral galaxies display a range of spheroid-to-total flux ratios
  from 0 to $\sim$3/4 (e.g.~\citealt{grahamworley2008}, and references
  therein), lenticular galaxies typically display a range from
  $\sim$3/4 to $\sim$0.1 \citep{laurikainen2010}.  This spheroid-to-total flux
  ratio is widely recognised as an important quantity, and its broad range observed in
  lenticular galaxies recently led to a re-introduction of 
  \citeauthor{vandenbergh1976}'s (\citeyear{vandenbergh1976})
  Hubble comb, in which both late-type galaxies (i.e.~spiral galaxies)
  and lenticular galaxies form separate arms of an expanded Hubble-Jeans tuning
  fork, with an additional arm for disc galaxies hosting anaemic spiral
  patterns \citep{cappellari2011kmdr,kormendybender2012}.  
  However because every spiral Hubble type (e.g.~Sa, Sb, Sc), not just the S0 galaxies, 
  has a broad range of spheroid-to-total ratio, and because this information is not captured by the Hubble comb, 
  a grid of spiral morphological type (predominantly determined by the spiral
  arms) versus spheroid-to-total ratio can also be useful for classifying galaxies.  \\
  In Figure \ref{fig:grid} we show the location of galaxies with intermediate-scale
  discs in such a ``Hubble grid'', which is effectively the quantitative scheme used by  
  \cite{boroson1981}, \cite{kent1985}, \cite{kodaira1986}, \cite{simiendevaucouleurs1986} 
  in which each galaxy type displays a range of spheroid-to-total flux ratio.
  Rather than a scheme in which the morphological type (a, b, c,
  etc.) changes if the spheroid-to-total ratio changes -- as in the Hubble comb -- here
  the galaxy type is linked to the nature and winding of the spiral arms
  which has been the primary criteria used to classify spiral galaxies
  over the last half century \citep{sandage1961}.  
  Allowing for the varying spheroid-to-total ratio among each galaxy type, 
  the Hubble grid helps to reveal how ellicular galaxies unify the early-type sequence and compare with late-type galaxies.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\columnwidth]{Hubblegrid.pdf}
  \caption{The Hubble grid \citep{graham2014review},
  which uses the mean pitch angle of the arms in spiral galaxies to define their morphological type.
  Ellicular (ES) galaxies are intermediate between elliptical (E) and lenticular (S0) galaxies. }
  \label{fig:grid}
  \end{center}
  \end{figure}

\section{Summary and conclusions}
{\bf Early-type galaxies display a broad distribution of spheroid-to-total flux ratios (e.g.~\citealt{cappellari2011}), 
going from disc-less, ``pure'' elliptical galaxies (slow rotators) 
to disc-dominated lenticular galaxies (central fast rotators that continue to be fast rotating also beyond one half-light radius). 
%\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
%vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
%simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,
%bendersaglia1999}\footnote{Many past studies were hampered by bulge/disc decompositions which forced an $R^{1/4}$ model for the bulge component 
%and thus obtained spurious bulge-to-disc ratios, and from the \emph{IRAF} task {\tt ellipse} which does not report the correct deviations of isophotes 
%from ellipses \citep{ciambur2015}.}. 
In between these two extremes lie galaxies with intermediate-scale discs 
(spheroid dominated central fast rotators that become slow rotating in their outer regions), 
i.e.~discs of kiloparsec-size that remain ``embedded'' within the spheroidal component of the galaxy 
and do not dominate the galaxy light at large radii as large-scale discs do. }
While this is likely known to some readers, 
the surge of papers presenting galaxy decompositions which are not aware of this reality 
has created a pressing need for this reminder. 
We have shown that the light distribution of galaxies with intermediate-scale discs can be accurately described 
with a simple spheroid + disc (+ optional nuclear component) model, 
without the need for the addition of a bright envelope-component. \\
Our decompositions correctly reproduce both the photometric (surface brightness and ellipticity profiles) 
and kinematic (specific angular momentum profile) properties of nine intermediate-scale disc galaxies. 
Four of these nine galaxies (Mrk 1216, NGC 1271, NGC 1277, NGC 1332) and one additional elliptical galaxy (NGC 4291) 
had previously been claimed to be extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
However, here we have demonstrated that, when correctly modelled, 
these five galaxies all reside well within the scatter of the correlation, 
i.e. they do not host over-massive black holes. 
This serves to strengthen the (black hole mass)-(spheroid mass) relation, 
and rules out the need for exotic formation scenarios.

### 2015-10-20 papers/mbhn/mbhn.tex
tue

%%
%% Beginning of file 'sample.tex'
%%
%% Modified 2005 December 5
%%
%% This is a sample manuscript marked up using the
%% AASTeX v5.x LaTeX 2e macros.

%% The first piece of markup in an AASTeX v5.x document
%% is the \documentclass command. LaTeX will ignore
%% any data that comes before this command.

%% The command below calls the preprint style
%% which will produce a one-column, single-spaced document.
%% Examples of commands for other substyles follow. Use
%% whichever is most appropriate for your purposes.
%%
%%\documentclass[12pt,preprint]{aastex}

%% manuscript produces a one-column, double-spaced document:

%\documentclass[manuscript]{aastex}

%% preprint2 produces a double-column, single-spaced document:

@@

\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{color}
\usepackage{hyperref}

%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
%% If you are submitting to a journal that translates manuscripts
%% into SGML, you need to follow certain guidelines when preparing
%% your macros. See the AASTeX v5.x Author Guide
%% for information.

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{gsavorgn@astro.swin.edu.au}

\newcommand{\fitfigurewidth}{0.8\textwidth}

%% You can insert a short comment on the title page using the command below.

%\slugcomment{Not to appear in Nonlearned J., 45.}

%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%% The left head contains a list of authors,
%% usually a maximum of three (otherwise use et al.).  The right
%% head is a modified title of up to roughly 44 characters.
%% Running heads will not print in the manuscript style.

@@

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

@@

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire.

@@

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, use \\ to force line breaks.

\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1}}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}

%\author{C. D. Biemesderfer\altaffilmark{4,5}}
%\affil{National Optical Astronomy Observatories, Tucson, AZ 85719}
\email{gsavorgn@astro.swin.edu.au}

%\and

%\author{A. W. Graham\altaffilmark{1}}
%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}

%% Notice that each of these authors has alternate affiliations, which
%% are identified by the \altaffilmark after each name.  Specify alternate
%% affiliation information with \altaffiltext, with one command per each
%% affiliation.

%\altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
%CTIO is operated by AURA, Inc.\ under contract to the National Science
%Foundation.}
%\altaffiltext{2}{Society of Fellows, Harvard University.}
%\altaffiltext{3}{present address: Center for Astrophysics,
%    60 Garden Street, Cambridge, MA 02138}
%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
%\altaffiltext{5}{Patron, Alonso's Bar and Grill}

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

@@

\section{Introduction}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
\caption{}
\label{fig:magn}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
\caption{}
\label{fig:mbhn}
\end{center}
\end{figure}

@@

%%
\acknowledgments

>>>>

@@

\bibliographystyle{apj}
\usepackage{natbib}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{color}
\usepackage{hyperref}

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{gsavorgn@astro.swin.edu.au}
\newcommand{\fitfigurewidth}{0.8\textwidth}

@@

@@

@@

\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1}}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
\email{gsavorgn@astro.swin.edu.au}

@@

\section{Introduction}
The empirical \cite{sersic1963,sersic1968} $R^{1/n}$ model has been demonstrated to provide adequate description 
of the light distribution of the stellar spheroidal and disk components of galaxies (add REFS), 
yet its physical origin has remained unexplained for decades. 
The S\'ersic model parametrizes the intensity $I$ as a function of the projected galactic radius $R$ such that
\begin{equation}
I(R; I_{\rm e},R_{\rm e},n) = I_{\rm e} \exp \biggl \{ -b_{\rm n} \biggl [ \Bigl (\frac{R}{R_{\rm e}} \bigr )^{1/n} -1 \biggr ] \biggr \}, 
\end{equation}
where $I_{\rm e}$ indicates the intensity at the effective radius $R_{\rm e}$ that encloses half of the total light from the model, 
the S\'ersic index $n$ is the parameter that regulates the curvature of the radial light profile, 
and $b_{\rm n}$ is a constant defined in terms of the S\'ersic index $n$ (see \citealt{grahamdriver2005}, and references therein). 
A large S\'ersic index corresponds to a steep central profile and a shallow outer profile, 
whereas a small S\'ersic index corresponds to a shallow central profile and a steep outer profile. 
This means that, for a stellar spheroidal system whose light distribution is well approximated by the S\'ersic model, 
the larger the S\'ersic index $n$ is, the more centrally concentrated the stars are and the more extended the outer envelope is. \\
A compelling physical interpretation for the S\'ersic profile family was recently theorized by \cite{cen2014} 
and later confirmed by \cite{nipoti2015} by means of $N$-body simulations. 
\cite{cen2014} conjectured that, when structures form within a standard cold dark matter model seeded by random Gaussian fluctuations, 
any centrally concentrated stellar structure always possesses an extended stellar envelope, and vice versa. 
\cite{nipoti2015} quantitatively explored Cen's hypothesis and showed that 
systems originated from several mergers have a large S\'ersic index ($n \gtrsim 4$), 
whereas systems with a S\'ersic index as small as $n \simeq 2$ can be produced by coherent dissipationless collapse, 
and exponential profiles ($n=1$) can only be obtained through dissipative processes.
This scenario sets the theoretical framework for the well known correlation between the spheroid luminosity, $L_{\rm sph}$,  
and the spheroid S\'ersic index, $n_{\rm sph}$, (e.g.~\citealt{youngcurrie1994,jerjen2000,grahamguzman2003}), 
although the numerical results of \cite{nipoti2015} seem to lack of spheroidal systems with $n$ as large as $7 - 10$, 
which are commonly observed in the local Universe.  \\
Given the existence of the $L_{\rm sph} - n_{\rm sph}$ correlation 
and the relation between the central black hole mass, $M_{\rm BH}$, and $L_{\rm sph}$ (e.g.~\citealt{magorrian1998}), 
an $M_{\rm BH} - n_{\rm sph}$ relation must exist. 
After \cite{graham2001} showed that the black hole mass is tightly linked to the stellar light concentration of spheroids 
(measured through a parameter different from but closely related to the S\'ersic index), 
\cite{grahamdriver2007} presented for the first time the $M_{\rm BH} - n_{\rm sph}$ correlation.

s+11 v+12 b+12  \\
my paper \\
paper I and II \\

@@

\begin{figure}[h]
\begin{center}
%\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
\caption{}
\label{fig:magn}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
%\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
\caption{}
\label{fig:mbhn}
\end{center}
\end{figure}

@@

%%
\acknowledgments
kkkkk
